Visualizing anesthesia-induced vasodilation of cerebral vasculature using multi-exposure speckle imaging

### 2020-06-16 article.tex
Implemented edits from L. L.

There have been numerous imaging modalities used to examine the effects of isoflurane on cerebral hemodynamics. Functional magnetic resonance imaging (fMRI), laser Doppler flowmetry, and intrinsic signal optical imaging have all established that isoflurane increases basal cerebral blood flow (CBF) while attenuating and delaying the hemodynamic response via neurovascular coupling \cite{Sicard:2003dj,Desai:2011mb,Aksenov:2015ea,Takuwa:2012ee,Pisauro:2013cx}. Two-photon phosphorescence lifetime microscopy showed that tissue oxygenation is twice as high under isoflurane anesthesia compared to the awake state and exhibited large layer-specific differences within the cortical vasculature \cite{Lyons:2016bd}. Calcium signal imaging following ischemic stroke found that the magnitude of spreading depolarizations were significantly smaller in awake mice \cite{Balbi:2017cj} while laser speckle contrast imaging (LSCI) during photothrombotic stroke induction observed larger infarct sizes in awake rats compared to their isoflurane-anesthetized counterparts \cite{Lu:2017bo}. To date, no study has directly monitored the induction of general anesthesia and its acute effects upon the cerebral vasculature.

@@

The 15 raw intensity images were converted to speckle contrast images ($K = \sigma_{s} / {\langle{I}\rangle}$) with a 7x7-pixel window and used to calculate an estimate of the speckle correlation time ($\tau_c$) at each pixel with the multi-exposure speckle visibility expression \cite{Parthasarathy:2008el}:
%
% Equation 1 - MESI Equation
\begin{equation}
    \label{eq:mesi}
    K(T,\tau_c) =
        \left(
        \beta\rho^2\frac{e^{-2x} - 1 + 2x}{2x^2} +
        4\beta\rho(1 - \rho)\frac{e^{-x} - 1 + x}{x^2} +
        \beta(1 - \rho)^2 +
        \nu_{ne} +
        \nu_{noise}
        \right)^{1/2}
\end{equation}

@@

Because $\tau_c$ is inversely related to the speed of the moving scatterers \cite{Bonner:1981hg,Briers:1996kfa}, the inverse correlation time ($ICT = 1/\tau_c$) is frequently used as a metric for quantifying blood flow in vasculature and perfusion in parenchyma \cite{Ayata:2004ba,Strong:2005kj,Sullender:2018ff}. Recent work to improve the quantitative accuracy of MESI flow measurements in vasculature takes into account the presence of multiple dynamic scattering events instead of assuming only a single dynamic scattering event per photon \cite{Kazmi:2015du}. This is achieved by scaling the fitted $ICT$ value by the diameter of the vessel in order to obtain an estimate of "vascular flux” that better accounts for variations in vascular volume sampling \cite{Kazmi:2015du,Richards:2017df}. This paper utilizes the vascular flux metric (arbitrary units) for all vessel measurements and $ICT$ (s$^{-1}$) for all parenchymal perfusion measurements.

@@

Mice ($n = 4$, C57BL/6J, male, 4-6 months, Charles River Laboratories, Inc.) were anesthetized with medical $O_2$ vaporized isoflurane (3\% for induction, 1-2\% for maintenance, 0.5 L/min) via nose-cone inhalation. Body temperature was maintained at 37 $^\circ$C with a feedback heating pad (DC Temperature Controller, Future Health Concepts, Inc.). Arterial oxygen saturation, heart rate, and breathing rate were monitored via pulse oximetry (MouseSTAT, Kent Scientific Corp.). Mice were placed supine in a stereotaxic frame (Kent Scientific Corp.) and subcutaneously administered carprofen (5 mg/kg) and dexamethasone (2 mg/kg) to reduce inflammation during the craniotomy procedure. The scalp was shaved and resected to expose the skull between the bregma and lambda cranial coordinates. A 3 mm diameter portion of the skull over the somatosensory cortex was removed with a dental drill (Ideal Microdrill, 0.8 mm burr, Fine Science Tools, Inc.) while under regular artificial cerebrospinal fluid (buffered pH 7.4) perfusion. A 3 mm round cover glass (\#1, World Precision Instruments, Inc.) was placed over the exposed brain with artificial cerebrospinal fluid filling the void. Gentle pressure was applied to the cover glass while Kwik-sil adhesive (World Precision Instruments, Inc.) was deposited to bond the glass to the skull. A layer of C\&B-Metabond (Parkell, Inc.) was applied over the Kwik-sil to create a sterile, air-tight seal around the craniotomy and to allow for the restoration of intracranial pressure. A second layer of C\&B-Metabond was used to cement a custom titanium head-plate centered around the cranial window for head-constrained awake measurements. The subjects were allowed to recover from surgery and monitored for cranial window integrity and normal behavior for at least four weeks prior to imaging. They were then exposed to head fixation during 20-30 minute sessions over 3-5 days until habituated to locomotion on a linear, belt-driven treadmill awake imaging system \cite{He:2020}.

@@

Cranial window implanted mice ($n = 3$) were head constrained on the awake imaging system and allowed to acclimate for 5-10 minutes. The awake hemodynamic baseline was then defined by acquiring 50 MESI frames, averaging the speckle contrast across each exposure time, and computing the corresponding $ICT$ frame using Eq.~(\ref{eq:mesi}). A custom 3D-printed inhalation nose-cone connected to the anesthesia vaporizer and scavenger was then placed several millimeters away from the subject and used to administer medical air (0.5 L/min) with no isoflurane (0\%). Continuous MESI was initiated ($t = 0$) and used to monitor the awake subject for 10 minutes before increasing isoflurane to 2.0\% to induce anesthesia. After one minute of exposure ($t = 11$ min), the nose-cone was fully positioned over the subject to ensure proper function. After two minutes of exposure ($t = 12$ min), a feedback heating pad (55-7030, Harvard Apparatus, Inc.) was placed beneath the subject to maintain a 37 $^\circ$C body temperature. The now anesthetized subject was continuously monitored with MESI until $t = 30$ min, at which point the anesthetized hemodynamic state was defined by acquiring and averaging an additional 50 MESI frames. The subject was then removed from the imaging system and allowed to recover from anesthesia on a heating pad before being transferred back into its cage. Each subject underwent three imaging sessions with at least one full day of recovery between each session.

@@

The systematic changes caused by general anesthesia with isoflurane are shown in Fig.~\ref{fig:system_image}b and Video 1. The visible decrease in speckle contrast and corresponding increase in MESI $ICT$ are representative of an increase in CBF caused by the vasodilatory effects of isoflurane \cite{Masamoto:2012bj}. Dilation can be seen across much of the surface vasculature, in particular the large central vein and numerous smaller vessels that have become more prominent in the anesthetized imagery as blood flow increased. These large alterations to the vasculature complicated image registration and precluded the generation of full-field relative flow change imagery.

@@

The temporal dynamics of the awake-to-anesthetized transition can be seen in Fig.~\ref{fig:acute}, where the change in blood flow within two veins and one parenchyma region were analyzed during the extended two-hour imaging session. The cross sections used to estimate $d_{vessel}$ are depicted in Fig.~\ref{fig:acute}a with the resulting changes in vessel diameter shown in Fig.~\ref{fig:acute}b. The width of the two vessels remained steady throughout the awake measurements but increased while under anesthesia, with the larger vessel (R1) growing by over 50\% after an hour of exposure. This vasodilation was also accompanied by an increase in blood flow as measured by the relative changes in vascular flux and parenchymal tissue perfusion (Fig.~\ref{fig:acute}c). The vascular flux in R1 and R2 increased by 267\% and 175\%, respectively, while the tissue perfusion in R3 grew by 161\%. The large deviation shortly after $t = 80$ min was caused by the subject briefly experiencing breathing difficulties that required the anesthesia to be reduced to 1.5\% isoflurane for several minutes. The breathing abnormality and change in anesthesia dosage had no apparent effects on the vessel size. Repeated measurements in the subject (Fig.~\ref{fig:acute}d-f) illustrate the stability of day-to-day MESI estimates of blood flow as well as the consistency of the hemodynamic response to isoflurane anesthesia.

% Figure 2 - Extended Awake to Anesthetized Measurements
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure2.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:acute}
        (a) Awake speckle contrast image overlaid with vascular (R1 and R2) and parenchyma (R3) regions used during flow analysis. Dashed lines indicate the cross-sectional profiles used to calculate vessel width (Scale bar = 1 mm). Timecourses of (b) vessel diameter and (c) relative change in blood flow within the regions over an extended two-hour imaging session. The vertical dashed line indicates the beginning of anesthesia induction. The relative vascular flux and tissue perfusion in (c) were computed using the average of the entire awake state for the baseline. Repeated measurements of (d) vessel diameter, (e) vascular flux, and (f) parenchyma tissue perfusion during awake and anesthetized states in the same animal over four imaging sessions (mean $\pm$ sd).
    }
\end{figure}

@@

\acknowledgments
This study was supported by the National Institutes of Health (Nos. EB011556 and NS108484).

>>>>

There have been numerous imaging modalities used to examine the effects of isoflurane on cerebral hemodynamics. Functional magnetic resonance imaging (fMRI), laser Doppler flowmetry, and intrinsic signal optical imaging have all established that isoflurane increases basal cerebral blood flow (CBF) while attenuating and delaying the hemodynamic response to local neural activity via neurovascular coupling \cite{Sicard:2003dj,Desai:2011mb,Aksenov:2015ea,Takuwa:2012ee,Pisauro:2013cx}. Two-photon phosphorescence lifetime microscopy showed that tissue oxygenation is twice as high under isoflurane anesthesia compared to the awake state and exhibited large layer-specific differences within the cortical vasculature \cite{Lyons:2016bd}. Calcium signal imaging following ischemic stroke found that the magnitude of spreading depolarizations were significantly smaller in awake mice \cite{Balbi:2017cj} while laser speckle contrast imaging (LSCI) during photothrombotic stroke induction observed larger infarct sizes in awake rats compared to their isoflurane-anesthetized counterparts \cite{Lu:2017bo}. However, to date, no study has directly monitored the induction of general anesthesia and its acute effects upon the cerebral vasculature.

@@

The 15 raw intensity images were converted to speckle contrast images ($K = \sigma_{s} / {\langle{I}\rangle}$) with a $7\times7$-pixel sliding window and used to calculate an estimate of the speckle correlation time ($\tau_c$) at each pixel with the multi-exposure speckle visibility expression \cite{Parthasarathy:2008el}:
%
% Equation 1 - MESI Equation
\begin{equation}
    \label{eq:mesi}
    K(T,\tau_c) =
        \left(
        \beta\rho^2\frac{e^{-2x} - 1 + 2x}{2x^2} +
        4\beta\rho(1 - \rho)\frac{e^{-x} - 1 + x}{x^2} +
        \beta(1 - \rho)^2 +
        \nu_{ne} +
        \nu_{noise}
        \right)^{1/2}
\end{equation}

@@

Because $\tau_c$ is inversely related to the speed of the moving scatterers \cite{Bonner:1981hg,Briers:1996kfa}, the inverse correlation time ($ICT = 1/\tau_c$) is frequently used as a metric for quantifying blood flow in vasculature and perfusion in parenchyma \cite{Ayata:2004ba,Strong:2005kj,Sullender:2018ff}. Recent work to improve the quantitative accuracy of MESI flow measurements in vasculature takes into account the presence of multiple dynamic scattering events instead of assuming only a single dynamic scattering event per photon \cite{Kazmi:2015du}. This is achieved by scaling the fitted $ICT$ value by the diameter of the vessel in order to obtain an estimate of "vascular flux” that better accounts for variations in vascular volume sampling \cite{Kazmi:2015du,Richards:2017df}. This paper uses the vascular flux metric (arbitrary units) for all vessel measurements and $ICT$ (s$^{-1}$) for all parenchymal perfusion measurements.

@@

Mice ($n = 4$, C57BL/6J, male, 4-6 months, Charles River Laboratories, Inc.) were anesthetized with medical $O_2$ vaporized isoflurane (3\% for induction, 1-2\% for maintenance, 0.5 L/min) via nose-cone inhalation. Body temperature was maintained at 37 $^\circ$C with a feedback heating pad (DC Temperature Controller, Future Health Concepts, Inc.). Arterial oxygen saturation, heart rate, and breathing rate were monitored via pulse oximetry (MouseSTAT, Kent Scientific Corp.). Mice were placed supine in a stereotaxic frame (Kent Scientific Corp.) and subcutaneously administered carprofen (5 mg/kg) and dexamethasone (2 mg/kg) to reduce inflammation during the craniotomy procedure. The scalp was shaved and resected to expose the skull between the bregma and lambda cranial coordinates. A 3 mm diameter portion of the skull over the somatosensory cortex was removed with a dental drill (Ideal Microdrill, 0.8 mm burr, Fine Science Tools, Inc.) while under regular artificial cerebrospinal fluid (buffered pH 7.4) perfusion. A 3 mm round cover glass (\#1, World Precision Instruments, Inc.) was placed over the exposed brain with artificial cerebrospinal fluid filling the void. Gentle pressure was applied to the cover glass while Kwik-sil adhesive (World Precision Instruments, Inc.) was deposited to bond the glass to the skull. A layer of C\&B-Metabond (Parkell, Inc.) was applied over the Kwik-sil to create a sterile, air-tight seal around the craniotomy and to allow for the restoration of intracranial pressure. A second layer of C\&B-Metabond was used to cement a custom titanium head-plate centered around the cranial window for head-constrained awake measurements. The subjects were allowed to recover from surgery and monitored for cranial window integrity and normal behavior for at least four weeks prior to imaging. They were then exposed to head fixation during 20-30 minute sessions over 3-5 days until habituated to locomotion on a linear treadmill awake imaging system \cite{He:2020}.

@@

Cranial window implanted mice ($n = 3$) were head constrained on the awake imaging system and allowed to acclimate for 5-10 minutes. The awake hemodynamic baseline was then defined by acquiring 50 MESI frames, averaging the speckle contrast across each exposure time, and computing the corresponding $ICT$ frame using Eq.~(\ref{eq:mesi}). A custom 3D-printed inhalation nose-cone connected to the anesthesia vaporizer and scavenger was then placed several millimeters away from the subject and used to administer medical air (0.5 L/min) with no isoflurane (0\%). Continuous MESI was initiated ($t = 0$) and used to monitor the awake subject for 10 minutes before increasing isoflurane to 2.0\% to induce anesthesia. After one minute of exposure ($t = 11$ min), the nose-cone was fully positioned over the subject to ensure targeted delivery of isoflurane to the subject. After two minutes of exposure ($t = 12$ min), a feedback heating pad (55-7030, Harvard Apparatus, Inc.) was placed beneath the subject to maintain a 37 $^\circ$C body temperature. The now anesthetized subject was continuously monitored with MESI until $t = 30$ min, at which point the anesthetized hemodynamic state was defined by acquiring and averaging an additional 50 MESI frames. The subject was then removed from the imaging system and allowed to recover from anesthesia on a heating pad before being transferred back into its cage. Each subject underwent three imaging sessions with at least one full day of recovery between each session.

@@

The systematic changes caused by general anesthesia with isoflurane are shown in Fig.~\ref{fig:system_image}b and Video 1, which highlights the transition from the awake to anesthetized state. The visible decrease in speckle contrast and corresponding increase in MESI $ICT$ are representative of an increase in CBF caused by the vasodilatory effects of isoflurane \cite{Masamoto:2012bj}. Dilation is seen across much of the surface vasculature, in particular the large central vein and numerous smaller vessels that have become more prominent in the anesthetized imagery as blood flow increased. These large alterations to the vasculature complicated image registration and precluded the generation of full-field relative flow change imagery.

@@

The temporal dynamics of the awake-to-anesthetized transition can be seen in Fig.~\ref{fig:acute}, where the change in blood flow within two veins and one parenchyma region were analyzed during the extended two-hour imaging session. The cross sections used to estimate $d_{vessel}$ are depicted in Fig.~\ref{fig:acute}a with the resulting changes in vessel diameter shown in Fig.~\ref{fig:acute}b. The width of the two vessels remained steady throughout the awake measurements but increased under anesthesia, with the larger vessel (R1) growing by over 50\% after an hour of exposure. This vasodilation was also accompanied by an increase in blood flow as measured by the relative changes in vascular flux and parenchymal tissue perfusion (Fig.~\ref{fig:acute}c). The vascular flux in R1 and R2 increased by 267\% and 175\%, respectively, while the tissue perfusion in R3 grew by 161\%. The large deviation shortly after $t = 80$ min was caused by the subject briefly experiencing breathing difficulties that required the anesthesia to be reduced to 1.5\% isoflurane for several minutes. The breathing abnormality and change in anesthesia dosage had no apparent effects on the vessel size. Repeated measurements in the subject (Fig.~\ref{fig:acute}d-f) illustrate the stability of day-to-day MESI estimates of blood flow as well as the consistency of the hemodynamic response to isoflurane anesthesia.

% Figure 2 - Extended Awake to Anesthetized Measurements
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure2.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:acute}
        (a) Awake speckle contrast image overlaid with vascular (R1 and R2) and parenchyma (R3) regions used during flow analysis. Dashed lines indicate the cross-sectional profiles used to calculate vessel width (Scale bar = 1 mm). Timecourses of (b) vessel diameter and (c) relative change in blood flow within the regions over an extended two-hour imaging session. The vertical dashed line indicates the beginning of anesthesia induction. The relative vascular flux and tissue perfusion in (c) were computed using the average of the entire awake state for the baseline. Repeated measurements of (d) vessel diameter, (e) vascular flux, and (f) parenchyma tissue perfusion during awake and anesthetized states in the same animal over four imaging sessions (mean $\pm$ sd). Calculated using 50 MESI frames acquired immediately before and after the continuous imaging session.
    }
\end{figure}

@@

\acknowledgments
This study was supported by the National Institutes of Health (Nos. EB011556, HL140153, NS108484, and NS109361).
